How is experience transformed into memory?

### 2018-09-03 paper/main.tex
working on methods [WIP]

\textbf{JRM STOPPED HERE}

\subsubsection*{Extracting events using a hidden Markov model}
The topic model timepoint-by-timepoint correlation matrices all exhibited a block-diagonal structure (with small off-diagonal values), suggesting that the models were comprised of a number of sequential `states' (or events, see Fig.~\corrmats). To capture this structure, we fit the video and each recall model using a hidden Markov model (HMM). Given a number of states or events ($k$), the HMM recovers a set of labels that segments consecutive timepoints into $k$ events ~\citep{Rabi89, BaldEtal17}. To implement this analysis, we used the BrainIAK toolbox \citep{BaldEtal17, Brainiak}.

>>>>

\subsubsection*{Parsing topic trajectories into events using Hidden Markov Models}

\textbf{JRM STOPPED HERE...MISSING INFO}
% don't need background or "logic"
% what was the actual optimization metric used?  e.g. what was the penalty parameter?  we should write out the optimization as an "argmax" equation...but need info from ACH about the penalty term

The topic model timepoint-by-timepoint correlation matrices all exhibited a block-diagonal structure (with small off-diagonal values), suggesting that the models were comprised of a number of sequential `states' (or events, see Fig.~\corrmats). To capture this structure, we fit the video and each recall model using a hidden Markov model (HMM). Given a number of states or events ($k$), the HMM recovers a set of labels that segments consecutive timepoints into $k$ events ~\citep{Rabi89, BaldEtal17}. To implement this analysis, we used the BrainIAK toolbox \citep{BaldEtal17, Brainiak}.
